Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-03-17 paper/evaluation.tex
New combined trails graphic.

Each study session began with a five minute standardized explanation of the task. Then, the participants were asked to perform a 3 minute proofreading task on separate but representative data using focused proofreading. The participants were allowed to ask questions during this time. The classifier did not matter in this case since the user interface was the same. The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment. After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.
\begin{figure*}[t]
\centering
\includegraphics[width=\linewidth]{gfx/ac4trails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the AC4 subvolume. All measurements are reported as median VI, the lower the better. We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle. In all cases, guided proofreading yields better results with fewer corrections.}
\label{fig:ac4trails}
\end{figure*}

>>>>

Each study session began with a five minute standardized explanation of the task. Then, the participants were asked to perform a 3 minute proofreading task on separate but representative data using focused proofreading. The participants were allowed to ask questions during this time. The classifier did not matter in this case since the user interface was the same. The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment. After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.
\begin{figure*}[t]
\centering
\includegraphics[width=\linewidth]{gfx/ac4trails_combined.pdf}
\caption{Performance comparison of Plaza's focused proofreading (red) and our guided proofreading (blue) on the AC4 subvolume. All measurements are reported as median VI, the lower the better. We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (green line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle. In all cases, guided proofreading yields better results with fewer corrections.}
\label{fig:ac4trails}
\end{figure*}
